Paper Results Section

### 2019-03-27 notebooks/paper_results_section.Rmd
updated counts w matrix

# There's at least one transformation that we're always gonna want to apply, namly the vector/scalar
# collapse where both are present in a signature.
los <- lapply(los, function(lofuns) {lapply(lofuns, combine_scalar_vector_where_appropriate)})
```

Get the counts.
```{r}
# argument counts
c_basic_df <- build_arg_count_df_from_lopkgs(los)

@@

Generate...
```{r}
xtable(null_na_fold_real_arg_counts)
xtable(null_na_fold_real_fun_counts)
```

@@

>>>>

# There's at least one transformation that we're always gonna want to apply, namly the vector/scalar
# collapse where both are present in a signature.
los <- lapply(los, function(lofuns) {lapply(lofuns, combine_scalar_vector_where_appropriate)})
# Figure out which ones are matrices. Remove if the analysis picks this up (and we rerun).
los_m <- lapply(los, function(lofun) lapply(lofun, distinguish_matrices_df))
```

Get the counts.
```{r}
# argument counts
c_basic_df <- build_arg_count_df_from_lopkgs(los_m)

@@

Generate...
```{r}
xtable(null_na_fold_real_arg_counts) %>% print(include.rownames=F)
xtable(null_na_fold_real_fun_counts) %>% print(include.rownames=F)
```

@@

Print top 10.
```{r}
format_df_for_print(poly_type_args[1:10,]) -> put_me
put_me
xtable(put_me) %>% print(include.rownames=F)
```

I think something funky is happening.
We should have matrix types, maybe I forgot.
Dealing with that now:
```{r}
# NOTE matrix stuff moved up, oopsie
```

Top sig time.
```{r}
# poly_type_args <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los, extract_poly_type_args))
# poly_type_args <- poly_type_args[order(-poly_type_args$count),] # sort by count
# poly_type_args$perc <- round(poly_type_args$count/sum(poly_type_args$count) * 100, 2)
```

Print top 10.
```{r}
# format_df_for_print(poly_type_args[1:10,]) -> put_me
# put_me
# xtable(put_me) %>% print(include.rownames=F)
```

```{r}
# sigs_df_vec <- get_fun_sigs_matching_pred_from_lopkg(los, pred=does_df_have_X_types, types_to_find=c("matrix", "vector/real"), strict=T)
```
